`traveltime`: an R package to calculate travel time across a landscape from user-specified locations

### 2025-05-05 paper/paper.qmd
use author block <https://github.com/kapsner/authors-block> extension to add author addresses and corresponding author to header in docx

---
title: "`traveltime`: an R package to calculate travel time across a landscape from user-specified locations"
format:
  # md: default
  # wordcount-html:
  # html:
  #   keep-md: true
  #   fig-height: 4
  #   fig-align: center
  #   fig-format: png
  #   dpi: 300
  #pdf:
  docx:
    keep-md: true
    fig-height: 6
    fig-align: center
    dpi: 600
    fig-format: jpeg
# header-includes:
#   \usepackage{lineno} \linenumbers
#   \usepackage{hanging}
tags: 
  - R
  - geographic information systems
  - spatial analysis
author:
  - name: Gerard E. Ryan
    orcid: 0000-0003-0183-7630
    corresponding: true
    affiliation: "1, 2"
  - name: Nicholas Tierney
    orcid: 0000-0003-1460-8722
    affiliation: "1, 3"
  - name: Nick Golding
    orcid: 0000-0001-8916-5570
    affiliation: "1, 4"
  - name: Daniel J. Weiss
    orcid: 0000-0002-6175-5648
    affiliation: "1, 3"
affiliations:
 - name: The Kids Research Institute Australia, Nedlands 6009 WA, Australia
   index: 1
 - name: Melbourne School of Population and Global Health, University of Melbourne, 3010, VIC, Australia
   index: 2
 - name: Curtin University, Bentley, WA, Australia
   index: 3
 - name: University of Western Australia, WA, Australia
   index: 4
date: 2025-05-02
bibliography: paper.bib
---

>>>>

---
title: "`traveltime`: an R package to calculate travel time across a landscape from user-specified locations"
format:
  # md: default
  # wordcount-html:
  # html:
  #   keep-md: true
  #   fig-height: 4
  #   fig-align: center
  #   fig-format: png
  #   dpi: 300
  #pdf:
  docx:
    keep-md: true
    fig-height: 6
    fig-align: center
    dpi: 300
    fig-format: png
# header-includes:
#   \usepackage{lineno} \linenumbers
#   \usepackage{hanging}
tags: 
  - R
  - geographic information systems
  - spatial analysis
author:
  - name: Gerard E. Ryan
    orcid: 0000-0003-0183-7630
    corresponding: true
    email: gerry.ryan@thekids.org.au
    #affiliation: "1, 2"
    affiliations:
      - ref: TKRIA
      - ref: MSPGH
  - name: Nicholas Tierney
    orcid: 0000-0003-1460-8722
    #affiliation: "1, 3"
    affiliations:
      - ref: TKRIA
      - ref: CU
  - name: Nick Golding
    orcid: 0000-0001-8916-5570
    #affiliation: "1, 4"
    affiliations:
      - ref: TKRIA
      - ref: UWA
  - name: Daniel J. Weiss
    orcid: 0000-0002-6175-5648
    #affiliation: "1, 3"
    affiliations:
      - ref: TKRIA
      - ref: CU
affiliations:
 - name: The Kids Research Institute Australia, Nedlands 6009 WA, Australia
   id: TKRIA
   index: 1
 - name: Melbourne School of Population and Global Health, University of Melbourne, 3010, VIC, Australia
   index: 2
   id: MSPGH
 - name: Curtin University, Bentley, WA, Australia
   index: 3
   id: CU
 - name: University of Western Australia, WA, Australia
   index: 4
   id: UWA
date: 2025-05-02
bibliography: paper.bib
filters:
  - authors-block
---
